My title

### 2024-11-03 paper/paper.qmd
first revision of word choice

In equation \ref{eq:logit}, each $\beta$ represents a coefficient determined through regression analysis. The variables chosen for this project are pollster, population type, and recency of the poll. Each predictor variable was carefully selected based on its significance in polling analysis and its correlation with voting trends. The identity of the polling organization is critical to our model, as each pollster may exhibit unique biases. Including Pollster as a fixed effect allows us to account for these variations without introducing unnecessary complexity. Population Type distinguishes among different groups surveyed (e.g., voters, likely voters) and helps in capturing generalizability. Categorizing polls as either recent or not ensures that more recent polls, which are better predictors of voting behavior closer to the election, receive appropriate emphasis. $Y_i$ denotes the predicted popular vote percentage for Kamala Harris in the $i$-th poll. $\epsilon_i$ is the Gaussian-distributed error term, accounting for residual variation in the model.

@@

The model operates under the assumption that residuals follow a Gaussian distribution, though this may not entirely capture extreme polling variances. Additionally, pollster effects are treated as fixed, which, while limiting the model’s ability to reflect dynamic shifts in polling methodologies, simplifies the model and reduces the risk of overfitting. Alternative specifications, including a hierarchical model with random intercepts for pollsters, were considered. However, the added complexity of this approach did not significantly improve predictive accuracy. The chosen GLM specification thus offered a balanced approach, optimizing both interpretability and performance, making it the preferred model for our study.

@@

Figure @fig-coefficient-estimates visually represents the model coefficients, with error bars indicating the confidence interval for each estimate. Positive coefficients suggest that specific pollsters or demographic characteristics increase Harris’s predicted vote share. For example, the 'CES / YouGov' pollster shows a significant positive impact, while 'Siena/NYT' has a slight negative effect. These error bars help contextualize the reliability of each predictor.

@@

Non-response bias is a significant concern in YouGov’s methodology. Individuals who opt out of surveys may systematically differ from those who participate. YouGov employs several strategies to mitigate this issue, including **post-survey weighting**, which adjusts the survey data to reflect population characteristics, and **imputation techniques**, which estimate missing responses based on patterns in the available data. Despite these efforts, non-response bias can still affect the accuracy of predictions, particularly when certain demographic groups (e.g., less-educated or low-trust individuals) are less likely to participate.

YouGov places emphasis on clear and concise survey design, reducing participant fatigue and improving data quality. Their surveys generally avoid overly complex or leading questions, which could skew results. However, question wording remains a critical area, as even subtle changes in phrasing can influence responses. For instance, YouGov’s research shows how question wording can significantly affect voter perception and reported support for policies. Additionally, longer surveys can lead to increased dropout rates, potentially introducing non-response bias. To combat this, YouGov often incorporates survey logic, dynamically adjusting questions based on prior responses to keep participants engaged.

YouGov’s panel-based methodology, combined with advanced statistical techniques like MRP, offers a robust approach to polling. Their methods effectively address many challenges associated with non-random sampling and non-response bias. However, limitations persist, particularly regarding the biases inherent in self-selection and question framing. Overall, while YouGov’s methodology is well-suited to large-scale surveys, particularly in politics, careful consideration of their sampling and non-response strategies is necessary to fully interpret their findings.

>>>>

In equation \ref{eq:logit}, each $\beta$ represents a coefficient determined through regression analysis. The variables chosen for this project are pollster, population type, and recency of the poll. Each predictor variable was carefully selected based on its significance in polling analysis and its correlation with voting trends. The identity of the polling organization is important to our model, as each pollster may exhibit unique biases. Including Pollster as a fixed effect allows us to account for these variations without introducing unnecessary complexity. Population Type distinguishes among different groups surveyed (e.g., voters, likely voters) and helps in capturing generalizability. Categorizing polls as either recent or not ensures that more recent polls, which are better predictors of voting behavior closer to the election, receive appropriate emphasis. $Y_i$ denotes the predicted popular vote percentage for Kamala Harris in the $i$-th poll. $\epsilon_i$ is the Gaussian-distributed error term, accounting for residual variation in the model.

@@

The model operates under the assumption that residuals follow a Gaussian distribution, though this may not entirely capture extreme polling variances. Additionally, pollster effects are treated as fixed, which, while limiting the model’s ability to reflect dynamic shifts in polling methodologies, simplifies the model and reduces the risk of overfitting. Alternative specifications, including a hierarchical model with random intercepts for pollsters, were considered. However, the added complexity of this approach did not much improve predictive accuracy. The chosen GLM specification thus offered a balanced approach, optimizing both interpretability and performance, making it the preferred model for our study.

@@

Figure @fig-coefficient-estimates visually represents the model coefficients, with error bars indicating the confidence interval for each estimate. Positive coefficients suggest that specific pollsters or demographic characteristics increase Harris’s predicted vote share. For example, the 'CES / YouGov' pollster shows a positive impact, while 'Siena/NYT' has a slight negative effect. These error bars help contextualize the reliability of each predictor.

@@

Non-response bias is one of the main concerns in YouGov’s methodology. Individuals who opt out of surveys may systematically differ from those who participate. YouGov employs several strategies to mitigate this issue, including post-survey weighting, which adjusts the survey data to reflect population characteristics, and imputation techniques, which estimate missing responses based on patterns in the available data. Despite these efforts, non-response bias can still affect the accuracy of predictions, particularly when certain demographic groups (e.g., less-educated or low-trust individuals) are less likely to participate.

YouGov focuses on clear and concise survey design, reducing participant fatigue and improving data quality. Surveys typically avoid overly complex or leading questions, which can skew the results. However, question-wording remains an important area, as even subtle changes in expression can affect responses. For example, YouGov's research shows how question-wording can affect voter perceptions and reported support for policies. Furthermore, prolonged surveys can lead to increased dropout rates, potentially resulting in non-response bias. To counteract this, YouGov often dynamically adjusts questions based on previous responses to keep participants engaged by incorporating survey logic.

YouGov’s panel-based methodology, combined with statistical techniques like MRP, offers a robust approach to polling. Their methods effectively address many challenges associated with non-random sampling and non-response bias. However, limitations persist, particularly regarding the biases inherent in self-selection and question framing. Overall, while YouGov’s methodology is well-suited to large-scale surveys, particularly in politics, careful consideration of their sampling and non-response strategies is necessary to fully interpret their findings.
